Plots for Latent Hawkes Paper

### 2020-09-22 output_scripts/Paper_Plots.Rmd
fix fig4b

```{r prepare data for 4b,cache=TRUE}
plot.s <- 7#9
plot.i <- 4
plot.j <- 5

@@

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0=mean(sim_model3_stan_sim1[[plot.s]]$lambda0[1001:2000]),
                       eta_1=mean(sim_model3_stan_sim1[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model3_stan_sim1[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model3_stan_sim1[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model3_stan_sim1[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model3_stan_sim1[[plot.s]]$f[1001:2000,],2,mean))
lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0=model1_par_est$lambda0,
                                     alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                    model1_par_est$f[plot.j],
                                    model1_par_est$eta_1,
                                    model1_par_est$eta_2,
                                    model1_par_est$eta_3),
                                    beta=model1_par_est$beta),
                                     events=temp.t,
                                     time.vec=time.segment)

## model2
#############
model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[plot.s]]$gamma[1001:2000,],2,mean),
                       zeta=apply(sim_model3_stan_sim2[[plot.s]]$zeta[1001:2000,],2,mean),
                       eta_1=mean(sim_model3_stan_sim2[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model3_stan_sim2[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model3_stan_sim2[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model3_stan_sim2[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model3_stan_sim2[[plot.s]]$f[1001:2000,],2,mean))

@@

```{r fig4b-recover-latent-states}
y.ub <- c(20,20,20)#c(130,72,31)
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 200#130
my.long.x <- 205#134.5
legend.x <- c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(20,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,10), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now ###
polygon(c(0,lambda.true$time.vec,200),
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,200),
        c(0,delta.positive,0),col=positive.col,border=NA)

@@

# model2
############
drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[2], 
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
                          box.type="n")
drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
                           model2_par_est$zeta[plot.j],
                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
                                                   model2_par_est$f[plot.j],
                                                   model2_par_est$eta_1,
                                                   model2_par_est$eta_2,
                                                   model2_par_est$eta_3),
                         beta=model2_par_est$beta,
                         events=test.mmhp$tau,
                         color=add.alpha(model_colors[2], alpha=line.alpha[2]),line.width=line.wdth[2])
legend(legend.x[2],legend.y[2],"C-DCHP",
       col = model_colors[2],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)

@@

legend(10,legend.y[2],c("State 1/0 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.1, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,4))
points(14,8,pch=1,cex=2,col="blue")
points(16,8,pch=16,cex=2,col="blue")

@@

plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), ylim=c(-3,10), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
polygon(c(0,lambda.true$time.vec,200), c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,200), c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

@@

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-12,8), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m3-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now
polygon(c(0,lambda.true$time.vec,200), c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,200), c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

@@

<!-- Not completed. This would need the rankings to be -->
<!-- rerun for all cohorts. -->

@@

<!-- Here is where I need to be a bit more careful about using the correct fits. -->
<!-- Currently using all from Jing's saved output. -->

<!-- In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices. -->

@@

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 150) +
  NULL
p3
```

>>>>

```{r prepare data for 4b,cache=TRUE}
plot.s <- 9#7#9
plot.i <- 4
plot.j <- 5

@@

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0 =
                         mean(sim_model3_stan_sim1[[plot.s]]$lambda0[1001:2000]),
                       eta_1=mean(sim_model3_stan_sim1[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model3_stan_sim1[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model3_stan_sim1[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model3_stan_sim1[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model3_stan_sim1[[plot.s]]$f[1001:2000,],2,mean))
lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
                                                   model1_par_est$lambda0,
                                    alpha =
                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                    model1_par_est$f[plot.j],
                                    model1_par_est$eta_1,
                                    model1_par_est$eta_2,
                                    model1_par_est$eta_3),
                                    beta=model1_par_est$beta),
                                     events=temp.t,
                                     time.vec=time.segment)

## model2
#############
model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[plot.s]]$gamma[1001:2000,],
                                   2,mean),
                    zeta = 
                      apply(sim_model3_stan_sim2[[plot.s]]$zeta[1001:2000,],2,mean),
                       eta_1=mean(sim_model3_stan_sim2[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model3_stan_sim2[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model3_stan_sim2[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model3_stan_sim2[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model3_stan_sim2[[plot.s]]$f[1001:2000,],2,mean))

@@

```{r fig4b-recover-latent-states}
y.ub <- c(20,20,20)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(50,50,50)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(20,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,10), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now ###
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.positive,0),col=positive.col,border=NA)

@@

# model2
############
drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[2], 
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
                          box.type="n")
drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
                           model2_par_est$zeta[plot.j],
                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
                                                   model2_par_est$f[plot.j],
                                                   model2_par_est$eta_1,
                                                   model2_par_est$eta_2,
                                                   model2_par_est$eta_3),
                         beta=model2_par_est$beta,
                         events=test.mmhp$tau,
                         color=add.alpha(model_colors[2],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])
legend(legend.x[2],legend.y[2],"C-DCHP",
       col = model_colors[2],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)

@@

legend(10,legend.y[2],c("State 0/1 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.1, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,4))
points(14,8,pch=1,cex=2,col="blue")
points(16,8,pch=16,cex=2,col="blue")

@@

plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), ylim=c(-3,10), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

@@

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-12,8), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m3-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

@@

@@

@@

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 150) + # aren't infinite but >150 and <200
  NULL
p3
```
